---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# AS7343

<!-- badges: start -->
<!-- badges: end -->

The goal of AS7343 is to simulate the response of the AS7343 spectral sensor
from asm OSRAM. Based on a light spectrum with high wavelength resolution
simulate the response of each of the 13 channels of the AS7343 digital spectral
sensor, or any other sensor. With the simulations of channels responses further
analysis will attempt to retrieve quantities of interest such as PAR, ePAR, 
UVA:PAR, R:FR and B:G ratios.

## Installation

You can install the development version of AS7343 with:

```{r, eval=FALSE}
remotes::install_github("aphalo/AS7343")
packageVersion("AS7343")
```

## Example

This is a basic example which shows you how to solve a common problem:

```{r example}
library(AS7343)
library(ggspectra)
simul_response(sun.spct, ams_AS7343.spct, 
               unit.out = "photon",
               scale.factor = 1e-6) |>
  ggplot(aes(spct.idx, .data[["R[/q]_Total"]])) +
  geom_col()
```


